### 2015-10-06 weeklyReport/motivating.tex
related
end of 10-5-15

\section{Example}
\noindent{\textbf{Drag-and-Drop support for systematic editing}}:

Consider a reuse task to implement a drag-and-drop plugin called \tool for Eclipse to support systematic editing~\cite{Meng:sydit11}. As shown in Figure~\ref{fig:clipboard}, users drag and drop the method they want to edit to \tool before editing. When they finish changing the method, they take another snapshot using drag-and-drop. \tool will automatically recommend locations that  are similar to the given example, and recommend similar but not identical edits based on similar context.

To complete this task, developer first queries Google code search (GCS) using the query \codefont{Eclipse plugin drag and drop to table}. We choose GCS because existing code example recommendation tools like Strathcona~\cite{Holmes:structural05} and code query tools like SNIFF~\cite{sniff:Sen09}  do not fit for such a medium scale reuse task. GCS returns 102 examples. We only analyze the first five returned examples because empirical evidence indicates that developers rarely look beyond this limit when searching~\cite{Starke:searchNum09}. The fourth example is much too long (over 1000 lines) without any explanation and the third and fifth example are duplicated with the first one. Figure~\ref{fig:dndweb} illustrates a snapshot for the first example returned by GCS. It implements a SWT shopping cart application to select items from all grocery items and put them into `My shopping cart' via drag-and-drop (Figure~\ref{fig:cartTable}). The second example implements an example for TODO labels which enables user to drag a TODO label from Editor Panel and drop it in an Eclipse Plugin List View (Figure~\ref{fig:todoList}). This is very similar to the task that requires to drag the source code from Editor Panel to an Eclipse Plugin View, yet we hope to use the table view to record multiple examples for both old version and new version, which is the format used in the first example.

Our next step is to extract common API calls for drag-and-drop action. It is always hard to distinguish the main functionality and variants via a single example, but with the help of multiple examples, our tool is able to identify the main API calls that provide desired functionality. In this example, we notice that the main API calls will be \{new Viewer(), setTransfer(), setOperation(), addDragSupport(), addDropSupport()\} given the hierarchical fact that both \codefont{TableViewer} and \codefont{ListViewer} are subclasses of \codefont{Viewer}.

After identifying the main API calls (and corresponding control structure), we investigate related elements for these API calls. The implementation of \{DropTargetListener, DragSourceListener\} are identified as common coupling elements, while \{TodoModelProvider, TableItem, GridLayout\} are excluded as they do not have corresponding mapping in the other example. We notice that we should override \{DropTargetListener.drop(), DragSourceListener.

\noindent{dragSetData()\} to help us finish the drag-and-drop reuse task.}

>>>>

\section{Motivating Example}

Consider that user wants to add undo and redo actions for their Java Swing text editor application with undo/redo buttons.  Without knowing any APIs, developer  first queries our tool with a free-form query \codefont{`java undo redo example'}. Our tool investigates top 10 web pages returned from Google, because empirical evidence indicates that developers rarely look beyond this limit when searching~\cite{Starke:searchNum09}. Our tool uses `expert' heuristic to filter and rank web pages: it favors pages that have complete code snippet and text description because these pages are more likely to be written by experts. Thus it removes 3 pages without explicit code snippets, and performs the initial parsing for the informal documentations to identify code-like terms.

\noindent{\textbf{Example collection phase.}} With 7  partial programs at hand, it first extracts class-level structural facts for each code example. Based on a relative match threshold to measure the relative occurrence of the number of matched facts out of all class-level facts,  our tool clusters these examples in three groups using complete linkage technique: 5 examples use classes in Java Swing like `AbstractAction' and `UndoableEditListener', another example uses a `Node' data structure to illustrate how to implement undo/redo actions using command design pattern, and the last example is the javadoc for `UndoManager'.  Our tool starts from the first cluster as it has the highest relative occurrence out of all examples. Based on partial program analysis, we generate a list of type facts to infer types and bind methods.

The common facts our tool extracts include: 
\begin{table}[ht]
\begin{center}
\caption{Common Structural Facts Extracted from the Examples }
\label{tab:total}
\vspace{1mm}
\scriptsize{
\begin{tabular*}{0.5\textwidth}{@{}l|l@{}} \hline
Level&Structural Facts\\\hline
class&subType(Undo*Action, AbstractAction), \\ 
&subType(Redo*Action, AbstractAction), \\
&subType(*Listener, UndoListener)\\ \hline
method&override(actionPerformed(), Undo*Action, AbstractAction), \\
&override(actionPerformed(), Redo*Action, AbstractAction), \\ \hline
statement&init(*,javax.swing.undo.UndoManager), \\
&invoke(UndoManager.undo, actionPerformed(), Undo*Action),\\
& invoke(UndoManager.redo, actionPerformed(), Redo*Action)\\  \hline
\end{tabular*}
 \label{tab:dataset}

We simplify some full names due to space limitation:

AbstractAction: javax.swing.AbstractAction;

UndoListener: javax.swing.event.UndoableEditListener

actionPerformed():actionPerformed(ActionEvent)
}
 \end{center}
\end{table}

\input{example}

\noindent{\textbf{Example clustering phase.}} After extracting facts for each example, our tool identifies main facts shared in all 5 examples shown in Figure~\ref{fig:fact} part A. It leverages slicing to group related facts. In this example, 3 of them add \codefont{Undo*Action} to \codefont{JMenuItem} by invoking \codefont{JMenuItem.add (ActionEvent)} and support undo and redo actions for Text Editor shown in Figure~\ref{fig:fact} part B. The other two of them invoke \codefont{JButton.addActionListener(ActionEvent)} to add these two actions to \codefont{JButton}, and support \codefont{JApplet} Shape drawing shown in Figure~\ref{fig:fact} part C. After extracting both main facts and related facts, we generate two reuse tasks by combining main facts with each related fact group.

\noindent{\textbf{Example integration phase.}} Given a context like Figure~\ref{fig:context} part D, our tool identifies the best-fit reuse task based on the number of matched facts in the user's context.  If our tool fails to identify any matched facts in the user's context, it will simply rank the reuse task based on its occurrence in the code examples. Our tool asks for user's selection by presenting the generated main facts and related facts to the user in the form of code snippet. 
After confirmed by users, our tool automatically fills the rest facts that do not exist in the context shown in Figure~\ref{fig:context} part E.

### 2015-10-06 weeklyReport/problem.tex
end of 10-5-15

Both location and integration of reusable examples are not trivial. First, for the phase of location, existing tools that search for specific API usage examples~\cite{MAPO:ECOOP09, Buse:apiICSE12, Export:DenysASE13, Sourcerer:SC14} might not be able to support such reuse tasks that always involve in multiple classes and related methods.  As a result, developers always query general search engine like Google or expert sites like StackOverflow to investigate potential tutorials for desired features. These search engines will return a list of informal documentations and users have to search for source code elements in these resources. Although some linking recovery  tools~\cite{PeterACE:ICSE13, RecoDoc:ICSE12} can help identify a partial program in the form of code snippet, they are not  sufficient to create a pragmatic reuse plan as the main functionality is always interleaving with auxiliary ones and  it is unlikely to find a `perfect' example that provides all desired features for the reuse task~\cite{Holmes:reuseStudy09}. Considering that a single example is not enough for a given task, developers need to investigate multiple example variants manually for the desired features (i.e., common API calls). Moreover, for the phase of integration, developers should not only  measure structural and semantic similarity between the example and target context for the main API calls that provide desired features~\cite{Cottrell:jigsaw08}, but also determine which unnecessary code should be eliminated to save maintenance cost~\cite{Holmes:ASE09, Holmes:reuse07} and which related elements should be transformed with structural correspondence~\cite{Cottrell:generalize07} to the target context. Unfortunately, for any selected example in non-trivial system, the number of structural dependencies to follow is much too large to be completely covered by developers. The partial programs~\cite{partialProgram:OOPSLA08} extracted from the location phase make it even harder to  tease out irrelevant elements  without knowing a full scenario of precise type information and method implementation details.  Finally, the location and integration phase can be iterative as there is no guarantee that a selected example will be appropriate until the integration results are examined.

To overcome these challenges, we propose to automatically identify common API calls that provide the main feature across different partial program examples from informal documentation, and integrate this reusable example to the target context with a set of related elements that are necessary to implement the main feature. We assume that the maximum set of overlapping API calls are the salient features that user intends to reuse based on the user query and the elements that are data dependent and control dependent on the common functionalities should interact with these APIs in a common way across different examples. Given a free-form query from users, our tool invokes search engine (e.g., Google) to obtain a list of partial programs by recovering links between code elements and informal resources, clusters these examples and extracts common API calls with corresponding control structures for each cluster, and integrate the user-chosen reuse plan to the target context with related elements that are dependent on the salient code elements. Our tool also lists a set of variants from multiple source code examples so that users can select features they prefer to reuse, and transforms chosen features to the target context.

Our approach helps identify and integrate reusable examples in three phases:
\begin{itemize}
\item \textbf{Example Collection Phase.} We identify the main features from multiple partial programs derived from informal resources. Without confined to an established code corpus to search for code examples, we leverage web search engine to obtain a list of tutorials in the form of partial programs~\cite{PeterACE:ICSE13, RecoDoc:ICSE12}. We use partial program analysis~\cite{partialProgram:OOPSLA08} to infer partial type and resolve syntactic ambiguity.

\item \textbf{Example Clustering Phase.} We cluster similar code examples together to reduce the duplicated code snippets . For each cluster, based on the partial type facts extracted in example collection phase,  we first identifying structural correspondence for the portions that are identical, similar but not identical, and different without correspondence~\cite{Cottrell:generalize07}. We then extract both identical and similar portions as common features, and regard the rest as alternative ones.

\item \textbf{Example Integration Phase.} Our approach investigates the user's contexts to recommend the best-fit example considering both structural and lexical similarity~\cite{Holmes:reuseStudy09}. After user's confirmation or user's selection, our approach integrates each structural correspondence to the target context~\cite{Cottrell:jigsaw08} with corresponding related elements. 
\end{itemize}

>>>>

Both location and integration of reusable examples are not trivial. For the phase of location, existing tools that search for specific API usage examples~\cite{MAPO:ECOOP09, Buse:apiICSE12, Export:DenysASE13, Sourcerer:SC14} might not be able to support such reuse tasks that always involve in multiple classes and related methods.  As a result, developers always query general search engines like Google or expert sites like StackOverflow to investigate potential tutorials for desired features. These search engines will return a list of informal documentations and users have to search for source code elements in these resources. Although some linking recovery  tools~\cite{PeterACE:ICSE13, RecoDoc:ICSE12} can help identify a partial program in the form of code snippet, they are not  sufficient to create a pragmatic reuse plan as the main functionality is always interleaving with auxiliary ones and  it is unlikely to find a `perfect' example that provides all desired features for the reuse task~\cite{Holmes:reuseStudy09}. Considering that a single example is not enough for a given task, developers need to investigate multiple example variants manually for the desired features (i.e., common API calls). For the phase of integration, developers should not only  measure structural and semantic similarity between the example and target context for the main API calls that provide desired features~\cite{Cottrell:jigsaw08}, but also determine which unnecessary code should be eliminated to save maintenance cost~\cite{Holmes:ASE09, Holmes:reuse07} and which related elements should be transformed with structural correspondence~\cite{Cottrell:generalize07} to the target context. Unfortunately, for any selected example in non-trivial system, the number of structural dependencies to follow is much too large to be completely covered by developers. The partial programs~\cite{partialProgram:OOPSLA08} extracted from the location phase make it even harder to  tease out irrelevant elements  without knowing a full scenario of precise type information and method implementation details.  Moreover,  the location and integration phase can be iterative as there is no guarantee that a selected example will be appropriate until the integration results are examined~\cite{Holmes:reuseStudy09}.

To overcome these challenges, we propose to automatically identify common API calls that provide the main feature across different partial program examples from informal documentation, and integrate this reusable example to the target context with a set of related elements that are necessary to implement the main feature. We assume that the overlapping API calls are the main features that the user intends to reuse based on the user query, and the related elements should be transformed to the target together with main features if they are data dependent and control dependent on the common functionalities in a common way across different examples. 
Figure~\ref{fig:system} illustrates the process of our system. 
Given a free-form query from users, our tool invokes search engine (e.g., Google) to obtain a list of partial programs by recovering links between code elements and informal resources, clusters these examples and extracts common structural facts (e.g., jQuery logical facts) with corresponding control structures for each cluster, identifies a set of related elements that interact with main elements in a common way,  constructs reuse task with both main elements and related elements and ranks them based on user's context, and finally integrates the reuse task selected by users to the target context.

%Our tool also lists a set of variants from multiple source code examples so that users can select features they prefer to reuse, and transforms chosen features to the target context.

Our approach helps identify and integrate reusable examples in three phases:
\begin{itemize}
\item \textbf{Example Collection Phase.} We identify the main features from multiple partial programs derived from informal resources. Without confined to an established code corpus, we leverage web search engine to obtain a list of code examples in the form of partial programs~\cite{PeterACE:ICSE13, RecoDoc:ICSE12}. We use partial program analysis~\cite{partialProgram:OOPSLA08} to infer partial type and resolve syntactic ambiguity.

\item \textbf{Example Clustering Phase.} We take three steps in this phase. Based on the type facts extracted from partial program analysis, we first cluster similar code examples based on the number of shared class-level facts to reduce the duplicated code snippets. Next, for each example in each cluster, we identify main facts that are shared among all examples, and perform slicing to identify related elements. We ignore the specific related elements that appear in a single example. Finally, we group the related elements based on their common interaction with main elements.

\item \textbf{Example Integration Phase.} Our approach investigates the user's contexts to recommend the best-fit reuse task  considering the number of matched structural facts in target context. After user's selection, our approach integrates the reuse task to the target context by transforming the unmatched structural facts based on matched facts in the context. 
\end{itemize}
